\newpage
\section{Analysis}

We plan to do the following analyses on the data

% Ordered list
\begin{enumerate}

   \item Correlation between time of day and activities?
        
        Do users commit more often at some particular time?

        \bigbreak
        
        This can be done for various kinds of GitHub activities:
           \begin{itemize}
                \item Commits
                \item Comments
                \item Opening of Issues
                \item Creation of Pull Requests
           \end{itemize}

    % \item What percentage of commits get reverted \\
    %       Is there a correlation between number of reverted commits and commit time 
    %       \bigbreak
      
    \item Lifespan of a project
            
          \begin{itemize}
              \item After what time period activities in a github project becomes stagnant or comes below a certain threshold.
              \item How, on an average, the frequency of commits varies for a project during its lifespan. %bellcurve ?
              \item Do project based on certain set of languages tend to have longer lifespan than others?
          \end{itemize}
      
    % \item What percentage of pull request get accepted?
        
    %       Is there a regional or national bias in terms of the number of pull requests accepted?

    \item Active User Acquisition Rate

        How has the number of active users changed over time? This will also need to consider users that later deleted their accounts or have made no contributions on the site.

        % This will require scanning the \code{users.csv} file and counting the month (of year) the user accounts were created in.
    
    \item Developer Countries
    
        Which countries do developers reside in and how has that data varied over time?
        
    \item Forks
        
        Is there a correlation between the number of times a project is forked and the languages used in that project?
    
    \item Most Active Users
    
        Who were the most active users for a range of time, what language they wrote code in.
        Activities can again be measured with commits, issues etc. \\
        Other parameters can be the number of followers a user has or the number of organizations he is a member of.
    
    \item How much of a project is community driven?
        
        What percentage of commits in a project were part of a pull request?
        or were authored by users who are not the creator of the project.
        
        After a project's creation, how much time does it take for the first community participation to occur?
        
\end{enumerate}
